State of the Practice for Lattice Boltzmann Method Software

### 2023-07-29 StateOfPractice/Papers/LatticeBoltz_SOP/LatticeBoltz_SOP.tex
Corrected postal code for Mechanical Engineering to match JHE building postal code

\affiliation[ME]{organization={McMaster University, Mechanical Engineering}, %Department and Organization
            addressline={1280 Main Street West}, 
            city={Hamilton},
            postcode={L8S 4K1}, 
            state={Ontario},
            country={Canada}}

>>>>

\affiliation[ME]{organization={McMaster University, Mechanical Engineering}, %Department and Organization
            addressline={1280 Main Street West}, 
            city={Hamilton},
            postcode={L8S 4L7}, 
            state={Ontario},
            country={Canada}}
